One-arm spirals in locally isothermal, radially structured self-gravitating discs

### 2014-11-09 paper/paper.tex
updated intro

% but also natural in GI. when/where does it happen? 
Spiral arms are also naturally associated with gravitational
instability in differentially rotating discs.

%original motivation for this work (DZGI)

%specifically m=1 (history, conditions)

>>>>

% but also natural in GI.
Spiral arms are also naturally associated with global gravitational 
instability (GI) of differentially rotating discs
\citep{goldreich65,laughlin96b,laughlin98,lodato05,forgan11}. Large-scale
spiral arms may provide significant angular momentum transport to enable
accretion \citep{lynden-bell72, papaloizou91,balbus99,lodato04}, and
spiral structures are potentially observable with the Atacama Large 
Millimeter/sub-millimeter Array \citep{cossins10,dipierror14}.

% when/where does it happen? formation stage/dead zones (special for ppd)
GI can be expected in the earliest stages of 
circumstellar disc formation \citep{kratter10b,inutsuka10,tsukamoto13}. %also
% outer parts  
In the case of protoplanetary discs, which have complex structure
\citep{armitage10}, GI may also occur in `dead
zones' --- sub-portions of the disc where the magneto-rotational
instability is ineffective for angular momentum transport
\citep{gammie96,turner08,landry13} and therefore has reduced mass
accretion. Dead zones may become
self-gravitating with sufficient mass built-up
\citep{armitage01,martin12,martin12b,zhu09,zhu10,zhu10b,bae13,bae14}.

% original motivation for this work (DZGI) 
Indeed, the original goal for this project was to clarify
what type of GI is relevant to astrophysical discs in which only part 
of it is self-gravitating, such as a protoplanetary disc containing a 
massive dead zone. However, our seemingly simple initial disc models
consistently produced one-armed spiral structures, despite not 
satisfying the usual requirements to generate them
(see below). We therefore dedicate this study to verify their origin.

%brief history of m=1 
%stellar wobble from indiana group 
Single-arm, or eccentric modes in

%this work  mechanism is not strictly sg

%this paper is organised as follows
